\plaintitle

### 2015-11-07 Paper/paper.tex
Added references on paper and bibtex file

There is a limited number of papers that specifically discuss SystemOne. These papers
mostly focus on the various modules that provide different kinds of functionality for SystemOne
and the features to be created rather than the speed and feasibility of the use of the system.
Suayan (1997) developed one of the first registration systems used in UPLB called the
UPLB RegisNet. This system was designed to automate the pre-enlistment of subjects for
students.

Meanwhile, the UPLB Academic Information System was created and had support for
modularity. Through its modularity, various modules were created for it. Cruz (2001) created a
Subjects module that gave it the ability to add, edit, and delete subjects from a list of subjects and
Almodiel (2001) developed a module that allowed teachers to add, search, and view the grades of
a student in their respective classes. Enrique (2001) then developed a Schedule of Classes
module that was responsible for managing and viewing the schedule of a subject, a room, or a
teacher.

After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
Registration System called SystemOne. This system was also extensible through modularity. In
this version, SystemOne used the Java programming language for implementing the Enlistor and
Registrar module, PHP 5 for the Department module and MySQL as the Database Management
System (DBMS).

@@

There was one study that focused on the speed and response time of SystemOne. Crespo
(2014) wrote a study entitled “Comparing the Response and Rendering Time of PHP-based
against Javascript-based SystemOne”. This study did a comparison on how much faster or slower
SystemOne would be had it been implemented in Javascript using the NodeJS interpreter. Her
study detailed the performance of her own Javascript-based implementation against the
PHP-based implementation. The results of her study showed that the Javascript-based
implementation yielded a 52 percent increase in overall speed.

@@

% % REFERENCES FORMAT
% % References must be the same font size as other body text.
% \bibliographystyle{sigchi}
% \bibliography{paper}

>>>>

There is a limited number of papers that specifically discuss SystemOne. These papers
mostly focus on the various modules that provide different kinds of functionality for SystemOne
and the features to be created rather than the speed and feasibility of the use of the system.
Suayan (1997) developed one of the first registration systems used in UPLB called the
UPLB RegisNet \cite{suayan}. This system was designed to automate the pre-enlistment of subjects for
students.

Meanwhile, the UPLB Academic Information System was created and had support for
modularity. Through its modularity, various modules were created for it. Cruz (2001) created a
Subjects module that gave it the ability to add, edit, and delete subjects from a list of subjects \cite{cruz} and
Almodiel (2001) developed a module that allowed teachers to add, search, and view the grades of
a student in their respective classes \cite{almodiel}. Enrique (2001) then developed a Schedule of Classes
module that was responsible for managing and viewing the schedule of a subject, a room, or a
teacher \cite{enrique}.

After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
Registration System called SystemOne \cite{javier}. This system was also extensible through modularity. In
this version, SystemOne used the Java programming language for implementing the Enlistor and
Registrar module, PHP 5 for the Department module and MySQL as the Database Management
System (DBMS).

@@

There was one study that focused on the speed and response time of SystemOne. Crespo
(2014) wrote a study entitled “Comparing the Response and Rendering Time of PHP-based
against Javascript-based SystemOne” \cite{crespo}. This study did a comparison on how much faster or slower
SystemOne would be had it been implemented in Javascript using the NodeJS interpreter. Her
study detailed the performance of her own Javascript-based implementation against the
PHP-based implementation. The results of her study showed that the Javascript-based
implementation yielded a 52 percent increase in overall speed.

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{sigchi}
\bibliography{paper}
